Title Goes Here

### 2020-04-10 analysis/paper/paper.Rmd
add more text

4. What are our methods?
- Framework: Bettinger&Eerkens
- Two models: Guided variation and Model-based bias =>  Multi-point Origin (in situ) and Single-point Origin (migration model)
- Test by Correlation and Variation (Pearson's r, PCA, Coefficient of Variation) 
- data collection, sites, artifact #
- attributes: landmarks (tps software)

5. What are our results? 
- overall change through time, grouping (chronology, typology)
- correlation
- PCA
- CV

6. What is the answer to our questions??
- low correlation + high variation? High correlation + low variation?
- How was SP spread in Korea, did they have single orgin or multiple origins?

7. What is limitation of this study?
- Maybe applying CV for SP is not ideal. It can be depending on individual knapper's skill and raw materials
- CV: lithis vs pottery

@@

Computing Pearson's correlation 
```{r}
# Correlations with significance levels
# I can move the library(pkg) to the top with other libraries but I'm leaving here for my reference for a while
library(Hmisc) 
rcorr(ML,BL, type = "pearson") # type can be pearson or spearman

>>>>

4. What are our methods?
- Framework: Bettinger&Eerkens
- Two models: Guided variation and Model-based bias =>  Multi-point Origin (in situ or in between one) and Single-point Origin (migration model)
- Test by Correlation and Variation (Pearson's r, PCA, Coefficient of Variation) 
- data collection, sites, artifact #
- attributes: landmarks (tps software)

5. What are our results? 
- overall change through time, grouping (chronology, typology)
- correlation: postively correlated(?)
- PCA: 2,3 phases are highly overlapped, high redundancy. The individual phase are scattered, low redundancy. Variables of Dimension 1 is positively correlated
- CV:values are around 20(ML)-34(SL). Compared to 2nd phase, 3rd phase has slightly lower variation.

6. What is the answer to our questions??
- low correlation + high variation? High correlation + low variation?
- What are the criteria for correlation and variation
- How was SP spread in Korea, did they have single orgin or multiple origins?

7. What is limitation of this study?
- Maybe applying CV for SP is not ideal. It can be depending on individual knapper's skill and raw materials
- CV of one site (SYG6) - no big difference with the value of all data
- CV: lithis vs pottery

- couldn't include thickness and weight

@@

Computing Pearson's correlation 
```{r}
# Correlations with significance levels
# I can move the library(pkg) to the top with other libraries but I'm leaving here for my reference for a while
library(Hmisc) 
rcorr(ML, BL, type = "pearson") # type can be pearson or spearman
